\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors

### 2021-08-02 main_cpc.tex

\begin{figure}
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_currents.png}
  \caption{Circular ring sheet current.}
  \label{fig:circular_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_fields.png}
  \caption{Circular ring magnetic field.}
  \label{fig:circular_ring_plot_fields}
\end{subfigure}

\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_currents.png}
  \caption{Square ring sheet current.}
  \label{fig:square_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_fields.png}
  \caption{Square ring magnetic field.}
  \label{fig:square_ring_plot_fields}
\end{subfigure}

>>>>

\begin{figure}
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
  \caption{Circular ring sheet current.}
  \label{fig:circular_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
  \caption{Circular ring magnetic field.}
  \label{fig:circular_ring_plot_fields}
\end{subfigure}

\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
  \caption{Square ring sheet current.}
  \label{fig:square_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
  \caption{Square ring magnetic field.}
  \label{fig:square_ring_plot_fields}
\end{subfigure}
